Collection of BAAD plots

### 2014-06-19 Rmd/baadplotscollection.Rmd
now works with new baad (where dataset was renamed to studyName)

# Roth2007 massive outlier, remove here
dat <- subset(dat, dataset != "Roth2007")

@@

pipe_bh <- summarize(group_by(dat, dataset, species), 
           alf_stbh=mean(a.lf / a.stbh, na.rm=TRUE),
           mlf_stbh=mean(m.lf / a.stbh, na.rm=TRUE),
           sla = mean(a.lf / m.lf, na.rm=TRUE),
           pft=first(pft),
           MAP=mean(MAP),
           MAT=mean(MAT),
           growingCondition=first(growingCondition),
           vegetation=first(vegetation))

@@

pipe_ba <- summarize(group_by(dat, dataset, species), 
                     alf_stba=mean(a.lf / a.stba, na.rm=TRUE),
                     mlf_stba=mean(m.lf / a.stba, na.rm=TRUE),
                     pft=first(pft),
                     MAP=mean(MAP),
                     MAT=mean(MAT),
                     growingCondition=first(growingCondition),
                     vegetation=first(vegetation))

@@

# baad2 : discard pot-grown plants
baad$Group <- paste(baad$dataset, baad$speciesMatched)
baad2 <- subset(baad, growingCondition %in% c("FW","PM","PU","FE"))
baad2$pft <- as.factor(baad2$pft)

@@

allombygroupandpftplot <- function(xvar, yvar, dataset, xlab=AxisLabels[[xvar]], 
                                   ylab=AxisLabels[[yvar]], 
                                   slopecomp=1, n_min=20,legend=FALSE,
                                   pftcols=list(EA="red", EG="hotpink", DA="blue")){

  dataset$X <- dataset[,xvar]
  dataset$Y <- dataset[,yvar]

  smfitsEA <- sma(Y ~ X*Group, data=subset(dataset,pft=="EA"), log='xy', n_min=n_min, quiet=TRUE)
  smfitsEG <- sma(Y ~ X*Group, data=subset(dataset,pft=="EG"), log='xy', n_min=n_min, quiet=TRUE)
  smfitsDA <- sma(Y ~ X*Group, data=subset(dataset,pft=="DA"), log='xy', n_min=n_min, quiet=TRUE)
  smfits <- sma(Y ~ X*Group, data=dataset, log='xy', n_min=n_min, quiet=TRUE)

@@

The following uses only dataset/species combinations that have at least 20 observations. Using `sma`, I fit leaf mass vs. plant height, and stem mass vs. plant height. From the coefficients of the fits we can calculate the size-dependent LMR relationship, which is not a log-log relationship (math will follow here).

@@

# Select datasets that have stem, leaf biomass, and height
x <- studyWithVars(baad, c("m.st","m.lf","h.t"))
x$dataset_species <- paste0(x$dataset,"_",x$species)

@@

# Add some metadata
dfr <- baad[,c("dataset","species","pft","vegetation","growingCondition")]
dfr$dataset_species <- with(dfr, paste0(dataset,"_",species))
dfr <- dfr[!duplicated(dfr$dataset_species),]
P <- merge(P, dfr)
P$pft <- as.factor(P$pft)
P$vegetation[is.na(P$vegetation)] <- "GH"
P$vegetation <- as.factor(P$vegetation)

@@

# nonfield <- union(which(P$vegetation == "GH"), which(P$dataset == "Poorter1999"))
nonfield <- which(P$growingCondition %in% c("CG","GH"))
field <- setdiff(1:nrow(P), nonfield)

@@

```{r warning=FALSE, message=FALSE, echo=FALSE}
getAttributeByStudy <- function(data, var, studies){
  i <- !is.na(data[[var]])
  data[c("dataset", var)][!duplicated(paste( data[["dataset"]], data[[var]])),]
}

>>>>

# Roth2007 massive outlier, remove here
dat <- subset(dat, studyName != "Roth2007")

@@

pipe_bh <- summarize(group_by(dat, studyName, species), 
           alf_stbh=mean(a.lf / a.stbh, na.rm=TRUE),
           mlf_stbh=mean(m.lf / a.stbh, na.rm=TRUE),
           sla = mean(a.lf / m.lf, na.rm=TRUE),
           pft=first(pft),
           MAP=mean(MAP),
           MAT=mean(MAT),
           growingCondition=first(growingCondition),
           vegetation=first(vegetation))

@@

pipe_ba <- summarize(group_by(dat, studyName, species), 
                     alf_stba=mean(a.lf / a.stba, na.rm=TRUE),
                     mlf_stba=mean(m.lf / a.stba, na.rm=TRUE),
                     pft=first(pft),
                     MAP=mean(MAP),
                     MAT=mean(MAT),
                     growingCondition=first(growingCondition),
                     vegetation=first(vegetation))

@@

# baad2 : discard pot-grown plants
baad$Group <- paste(baad$studyName, baad$speciesMatched)
baad2 <- subset(baad, growingCondition %in% c("FW","PM","PU","FE"))
baad2$pft <- as.factor(baad2$pft)

@@

allombygroupandpftplot <- function(xvar, yvar, studyName, xlab=AxisLabels[[xvar]], 
                                   ylab=AxisLabels[[yvar]], 
                                   slopecomp=1, n_min=20,legend=FALSE,
                                   pftcols=list(EA="red", EG="hotpink", DA="blue")){

  studyName$X <- studyName[,xvar]
  studyName$Y <- studyName[,yvar]

  smfitsEA <- sma(Y ~ X*Group, data=subset(studyName,pft=="EA"), log='xy', n_min=n_min, quiet=TRUE)
  smfitsEG <- sma(Y ~ X*Group, data=subset(studyName,pft=="EG"), log='xy', n_min=n_min, quiet=TRUE)
  smfitsDA <- sma(Y ~ X*Group, data=subset(studyName,pft=="DA"), log='xy', n_min=n_min, quiet=TRUE)
  smfits <- sma(Y ~ X*Group, data=studyName, log='xy', n_min=n_min, quiet=TRUE)

@@

The following uses only studyName/species combinations that have at least 20 observations. Using `sma`, I fit leaf mass vs. plant height, and stem mass vs. plant height. From the coefficients of the fits we can calculate the size-dependent LMR relationship, which is not a log-log relationship (math will follow here).

@@

# Select datasets that have stem, leaf biomass, and height
x <- studyWithVars(baad, c("m.st","m.lf","h.t"))
x$dataset_species <- paste0(x$studyName,"_",x$species)

@@

# Add some metadata
dfr <- baad[,c("studyName","species","pft","vegetation","growingCondition")]
dfr$dataset_species <- with(dfr, paste0(studyName,"_",species))
dfr <- dfr[!duplicated(dfr$dataset_species),]
P <- merge(P, dfr)
P$pft <- as.factor(P$pft)
P$vegetation[is.na(P$vegetation)] <- "GH"
P$vegetation <- as.factor(P$vegetation)

@@

nonfield <- which(P$growingCondition %in% c("CG","GH"))
field <- setdiff(1:nrow(P), nonfield)

@@

```{r warning=FALSE, message=FALSE, echo=FALSE}
getAttributeByStudy <- function(data, var, studies){
  i <- !is.na(data[[var]])
  data[c("studyName", var)][!duplicated(paste( data[["studyName"]], data[[var]])),]
}
